Inference methods comparison for the simplified Naomi model

### 2023-01-19 src/naomi-simple_compare/comparison.Rmd
Strange histograms for hyperparameters
Fix TMB hyper sampling, and fix mislabel of axis in KS comparison plots

ggplot(ks_summary, aes(x = `KS(TMB, tmbstan)`, y = `KS(aghq, tmbstan)`)) +
  geom_point(alpha = 0.5) +
  xlim(0, 1) +
  ylim(0, 1) +
  geom_abline(intercept = 0, slope = 1, linetype = "dashed") +
  labs(x = "KS(aghq, tmbstan)", y = "KS(TMB, tmbstan)") +
  theme_minimal()

@@

>>>>

ggplot(ks_summary, aes(x = `KS(TMB, tmbstan)`, y = `KS(aghq, tmbstan)`)) +
  geom_point(alpha = 0.5) +
  xlim(0, 1) +
  ylim(0, 1) +
  geom_abline(intercept = 0, slope = 1, linetype = "dashed") +
  labs(x = "KS(TMB, tmbstan)", y = "KS(aghq, tmbstan)") +
  theme_minimal()

@@

## Investigation into large KS values

The following parameters have KS values greater than 0.5 in both dimensions.

```{r}
(big_ks <- ks_summary %>%
  filter(`KS(aghq, tmbstan)` > 0.5, `KS(TMB, tmbstan)` > 0.5) %>%
  pull(Parameter))
```

Let's look into this further by plotting the histograms:

```{r}
lapply(big_ks, histogram_plot)
```
